---
title: "Capstone_data_support_landscape"
format: html
editor: visual
---

setwd
```{r}
setwd("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/")
```
# load libraries
```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(ggtext)
library(readxl)
```

# read in the data
```{r}
library(readxl)
library(readr)
df <- read_csv("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/capstone_data - Sheet1 (6).csv", skip = 2)

```
# Rename
Librarian_AB	
Librarian_GW	
Librarian_Me	
Librarian_MK	
Librarian_SM	
Librarian_SR	
Librarian_FH
Librarian_SW
Professor_TF
Professor_YK
Staff_JP

```{r}
# rename variables
# rename(df, new_name = old_name)        

rename(df, Title_Person = Person_title)
```

9-23-2026 Google AI mode
library(dplyr)

# Sample Data
df <- data.frame(status = c("A", "B", "C", "A"))

# Create a new column with renamed values
df <- df %>% 
  mutate(status_full = case_match(status,
    "A" ~ "Active",
    "B" ~ "Pending",
    "C" ~ "Cancelled",
    .default = status # Keeps original value if no match is found
  ))
  
```{r}

```
  

```{r}
# Read just the very first row
# second_row <- read_csv("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/capstone_data - Sheet1 (3).csv", n_max = 1, col_names = FALSE)
# top_row <- read_csv("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/capstone_data - Sheet1 (3).csv", skip = 1, n_max = 1, col_names = FALSE)
# 
# # Create a named vector acting as a dictionary (key-value map)
# # Assumes row 1 has descriptions/keys and row 2 has the standard names or vice versa
# my_dict <- as.list(top_row)
# names(my_dict) <- as.character(second_row)

# Example lookup: my_dict[["ColumnName"]]
```

Read in the data with header issues resolved
```{r}
# # library(readxl)
# # capstone_data <- read_excel("T:/JungMee/ICPSR_data/Providing_data_services/capstone_data - Sheet1.csv.xlsx")
# 
# # 1. Read the first two rows as raw data (no headers)
# header_rows <- read_csv("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/capstone_data - Sheet1 (3).csv", n_max = 2, col_names = FALSE)
# 
# # 2. Concatenate/combine the two rows element-wise using paste
# new_names <- apply(header_rows, 2, paste, collapse = "_")
# 
# # 3. Read the rest of the file, skipping the first two rows, and assign new names
# df <- read_csv("T:/JungMee/ICPSR_data/Providing_data_services/ICPSR Capstone/capstone_data - Sheet1 (3).csv", skip = 2, col_names = new_names)
```

remove top 2 rows in R
```{r}
# df <- capstone_data_raw[-c(1:2), ]
```


rename a value in a cell
```{r}
# df[1, 1] <- "Librarian_Me"
```


write csv of this version
```{r}
# write.csv(df, "capstone_data_correct_header.csv", row.names = FALSE)
```

```{r}
# library(ggplot2)
# library(readr)
# library(dplyr)
# 
# # --- Load data ---------------------------------------------------------
# # df <- read_csv("capstone_data_correct_header.csv")
# 
# First two columns, referenced by position (robust to header changes)
x_col <- names(df)[1]
y_col <- names(df)[2]

df <- df %>%
  rename(x = 1, y = 2)


# df$y <- as.numeric(df$y)
```

# Bar chart for activities
```{r}
# --- Bar chart -----------------------------------------------------------
p <- ggplot(df, aes(x = reorder(x, -y), y = y, fill = y)) +
  geom_col(color = "black", width = 0.7) +
  geom_text(aes(label = paste0(y, "%")), vjust = -0.5, fontface = "bold", size = 3.5) +
  scale_fill_viridis_c(name = y_col, guide = "none") +
  labs(
    title = "Percentage Time Allocated by Person",
    x = "Title of PersonPercentage of Work Hours",
    y = "Percentage of Work Hours"
  ) +
  ylim(0, max(df$y) * 1.15) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.title = element_text(face = "bold")
  )


print(p)

ggsave("bar_chart_R.png", plot = p, width = 10, height = 6, dpi = 150)

```

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)

# --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")
df <- df %>%
  rename(Person_title = 1, y = 2)

# --- Reshape: grab Person_title + all "Collecting and discovery_*" columns ---
plot_df <- df %>%
  select(Person_title, starts_with("Collecting and discovery_")) %>%
  pivot_longer(
    cols = -Person_title,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Collecting and discovery_"),
    # Order the ordinal levels RARE < TOUCH < DO, and map to a numeric score
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE),
    Level_num = as.numeric(Level)   # RARE = 1, TOUCH = 2, DO = 3
  )

# ============================================================================
# HEATMAP
# ============================================================================
p_heatmap <- ggplot(plot_df, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  labs(
    title = "Collecting and Discovery: Involvement by Person",
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

print(p_heatmap)
ggsave("collecting_discovery_heatmap.png", plot = p_heatmap, width = 10, height = 6, dpi = 150)


```

```{r}
# ============================================================================
# BUBBLE CHART (size + color both encode the ordinal level)
# ============================================================================
# p_bubble <- ggplot(plot_df, aes(x = Activity, y = Person_title)) +
#   geom_point(aes(size = Level_num, color = Level), alpha = 0.85) +
#   scale_size_continuous(range = c(2, 10), guide = "none") +
#   scale_color_manual(
#     values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
#     name = "Involvement"
#   ) +
#   labs(
#     title = "Collecting and Discovery: Involvement by Person",
#     x = "Activity",
#     y = "Person"
#   ) +
#   theme_minimal(base_size = 12) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1),
#     panel.grid.minor = element_blank(),
#     plot.title = element_text(face = "bold")
#   )
# 
# print(p_bubble)
# ggsave("collecting_discovery_bubble.png", plot = p_bubble, width = 10, height = 6, dpi = 150)
```



```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(ggtext)   # install.packages("ggtext") -- enables per-label bold/color on axis text

# --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")

# --- Reshape: grab Person_title + all "Collecting and discovery_*" columns ---
plot_df <- df %>%
  select(x, starts_with("Collecting and discovery_")) %>%
  pivot_longer(
    cols = -x,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Collecting and discovery_"),
    # Order the ordinal levels RARE < TOUCH < DO, and map to a numeric score
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE),
    Level_num = as.numeric(Level)   # RARE = 1, TOUCH = 2, DO = 3
  )

# ============================================================================
# HEATMAP  (with Librarian_Me highlighted)
# ============================================================================
highlight_person <- "Librarian_Me"

# Preserve a fixed row order so we can compute the highlighted row's y-position
person_levels <- unique(plot_df$x)
plot_df <- plot_df %>%
  mutate(Person_title = factor(x, levels = person_levels))

n_activities <- n_distinct(plot_df$Activity)
highlight_y <- which(person_levels == highlight_person)

# Bold the one axis label using markdown syntax (rendered via ggtext::element_markdown)
y_labels <- ifelse(person_levels == highlight_person,
                    paste0("**", person_levels, "**"),
                    person_levels)

p_heatmap <- ggplot(plot_df, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  # Black border box around the highlighted person's row
  annotate(
    "rect",
    xmin = 0.5, xmax = n_activities + 0.5,
    ymin = highlight_y - 0.5, ymax = highlight_y + 0.5,
    fill = NA, color = "black", linewidth = 1.2
  ) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  scale_y_discrete(labels = y_labels) +
  labs(
    title = "Collecting and Discovery: Involvement by Person",
    subtitle = paste0(highlight_person, " highlighted"),
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_markdown(),   # allows the ** bold ** markdown to render
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

print(p_heatmap)
ggsave("collecting_discovery_heatmap.png", plot = p_heatmap, width = 10, height = 6, dpi = 150)

# # ============================================================================
# # OPTION 2: BUBBLE CHART (size + color both encode the ordinal level)
# # ============================================================================
# p_bubble <- ggplot(plot_df, aes(x = Activity, y = Person_title)) +
#   geom_point(aes(size = Level_num, color = Level), alpha = 0.85) +
#   scale_size_continuous(range = c(2, 10), guide = "none") +
#   scale_color_manual(
#     values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
#     name = "Involvement"
#   ) +
#   labs(
#     title = "Collecting and Discovery: Involvement by Person",
#     x = "Activity",
#     y = "Person"
#   ) +
#   theme_minimal(base_size = 12) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1),
#     panel.grid.minor = element_blank(),
#     plot.title = element_text(face = "bold")
#   )
# 
# print(p_bubble)
# ggsave("collecting_discovery_bubble.png", plot = p_bubble, width = 10, height = 6, dpi = 150)
```
## Collecting and Discovery
```{r}
# library(ggplot2)
library(forcats)
# 
# ggplot(df, aes(x = x_variable, y = fct_rev(factor(y_variable)))) +
#   geom_point() +
#   labs(y = "Alphabetical Y-Axis")
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(stringr)

# --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")
df <- df %>%
  rename(x = 1, y = 2)
# --- Reshape: grab Person_title + all "Collecting and discovery_*" columns ---
plot_df <- df %>%
  select(x, starts_with("Collecting and discovery_")) %>%
  pivot_longer(
    cols = -x,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Collecting and discovery_"),
    # Order the ordinal levels RARE < TOUCH < DO
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
  )

# ============================================================================
# HEATMAP  (with Librarian_Me's axis label bolded + colored to highlight it)
# ============================================================================
highlight_person <- "Librarian_Me"

# Preserve a fixed row order so label order matches the data
person_levels <- unique(plot_df$x)
plot_df <- plot_df %>%
  mutate(Person_title = factor(x, levels = person_levels))

# Per-label styling vectors -- no extra packages needed.
# ggplot2 (>= 3.3) supports vectorized axis.text elements, applied in the
# same order as the axis breaks (person_levels here).
label_faces  <- ifelse(person_levels == highlight_person, "bold", "plain")
label_colors <- ifelse(person_levels == highlight_person, "black", "darkgrey")

p_heatmap <- ggplot(plot_df, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  labs(
    title = "Collecting and Discovery: Involvement by Person",
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(face = label_faces, colour = label_colors),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

p_heatmap
ggsave("collecting_discovery_heatmap.png", plot = p_heatmap, width = 10, height = 6, dpi = 150)
```

## Exploration and Analysis
```{r}

# --- Reshape: grab Person_title + all "Exploration and analysis_*" columns ---
plot_df2 <- df %>%
  select(x, starts_with("Exploration and analysis_")) %>%
  pivot_longer(
    cols = -x,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Exploration and analysis_"),
    # Order the ordinal levels RARE < TOUCH < DO
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
  )

# ============================================================================
# HEATMAP  (with Librarian_Me's axis label bolded + colored to highlight it)
# ============================================================================
highlight_person <- "Librarian_Me"

# Preserve a fixed row order so label order matches the data
person_levels <- unique(plot_df$x)
plot_df2 <- plot_df2 %>%
  mutate(Person_title = factor(x, levels = person_levels))

# Per-label styling vectors -- no extra packages needed.
# ggplot2 (>= 3.3) supports vectorized axis.text elements, applied in the
# same order as the axis breaks (person_levels here).
label_faces  <- ifelse(person_levels == highlight_person, "bold", "plain")
label_colors <- ifelse(person_levels == highlight_person, "black", "darkgrey")

p_heatmap2 <- ggplot(plot_df2, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  labs(
    title = "Exploration and Analysis: Involvement by Person",
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(face = label_faces, colour = label_colors),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

print(p_heatmap2)
ggsave("exploration_analysis_heatmap.png", plot = p_heatmap2, width = 10, height = 6, dpi = 150)
```

## Publishing and preserving
```{r}
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(stringr)

# --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")

# --- Reshape: grab Person_title + all "Publishing and preserving_*" columns ---
plot_df3 <- df %>%
  select(x, starts_with("Publishing and preserving_")) %>%
  pivot_longer(
    cols = -x,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Publishing and preserving_"),
    # Order the ordinal levels RARE < TOUCH < DO
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
  )

# ============================================================================
# HEATMAP  (with Librarian_Me's axis label bolded + colored to highlight it)
# ============================================================================
highlight_person <- "Librarian_Me"

# Preserve a fixed row order so label order matches the data
person_levels <- unique(plot_df3$x)
plot_df3 <- plot_df3 %>%
  mutate(Person_title = factor(x, levels = person_levels))

# Per-label styling vectors -- no extra packages needed.
# ggplot2 (>= 3.3) supports vectorized axis.text elements, applied in the
# same order as the axis breaks (person_levels here).
label_faces  <- ifelse(person_levels == highlight_person, "bold", "plain")
label_colors <- ifelse(person_levels == highlight_person, "black", "darkgrey")

p_heatmap3 <- ggplot(plot_df3, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  labs(
    title = "Publishing and Preserving: Involvement by Person",
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(face = label_faces, colour = label_colors),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

print(p_heatmap3)
ggsave("publishing_preserving_heatmap.png", plot = p_heatmap3, width = 10, height = 6, dpi = 150)
```

```{r}
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(stringr)

# --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")

# --- Reshape: grab Person_title + all "Type of data_*" columns ---
plot_df4 <- df %>%
  select(x, starts_with("Type of data_")) %>%
  pivot_longer(
    cols = -x,
    names_to = "Activity",
    values_to = "Level"
  ) %>%
  mutate(
    # Strip the "Collecting and discovery_" prefix for cleaner labels
    Activity = str_remove(Activity, "^Type of data_"),
    # Order the ordinal levels RARE < TOUCH < DO
    Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
  )

# ============================================================================
# HEATMAP  (with Librarian_Me's axis label bolded + colored to highlight it)
# ============================================================================
highlight_person <- "Librarian_Me"

# Preserve a fixed row order so label order matches the data
person_levels <- unique(plot_df4$x)

plot_df4 <- plot_df4 %>%
  mutate(Person_title = factor(x, levels = person_levels))

# Per-label styling vectors -- no extra packages needed.
# ggplot2 (>= 3.3) supports vectorized axis.text elements, applied in the
# same order as the axis breaks (person_levels here).
label_faces  <- ifelse(person_levels == highlight_person, "bold", "plain")
label_colors <- ifelse(person_levels == highlight_person, "black", "darkgrey")

p_heatmap4 <- ggplot(plot_df4, aes(x = Activity, y = Person_title, fill = Level)) +
  geom_tile(color = "white", linewidth = 0.6) +
  scale_fill_manual(
    values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
    name = "Involvement"
  ) +
  labs(
    title = "Type of Data: Involvement by Person",
    x = "Activity",
    y = "Person"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(face = label_faces, colour = label_colors),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold")
  )

p_heatmap4
ggsave("type_of_data_heatmap.png", plot = p_heatmap4, width = 10, height = 6, dpi = 150)
```


```{r}
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(stringr)
# library(ggtext)   # install.packages("ggtext") if you haven't -- then RESTART R
# 
# # --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")
# 
# # --- Reshape: grab Person_title + all "Collecting and discovery_*" columns ---
# plot_df <- df %>%
#   select(Person_title, starts_with("Collecting and discovery_")) %>%
#   pivot_longer(
#     cols = -Person_title,
#     names_to = "Activity",
#     values_to = "Level"
#   ) %>%
#   mutate(
#     # Strip the "Collecting and discovery_" prefix for cleaner labels
#     Activity = str_remove(Activity, "^Collecting and discovery_"),
#     # Order the ordinal levels RARE < TOUCH < DO
#     Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
#   )
# 
# # ============================================================================
# # HEATMAP  (Librarian_Me's axis label gets a yellow highlighter box, no bold)
# # ============================================================================
# highlight_person <- "Librarian_Me"
# 
# # Preserve a fixed row order so label order matches the data
# person_levels <- unique(plot_df$Person_title)
# plot_df <- plot_df %>%
#   mutate(Person_title = factor(Person_title, levels = person_levels))
# 
# # Wrap only the target label in a <span> with a yellow background.
# # No <b> tag this time -- font stays regular weight.
# y_labels <- ifelse(
#   person_levels == highlight_person,
#   paste0("<span style='background-color:#ffe600; padding:2px 4px;'>", person_levels, "</span>"),
#   person_levels
# )
# 
# p_heatmap <- ggplot(plot_df, aes(x = Activity, y = Person_title, fill = Level)) +
#   geom_tile(color = "white", linewidth = 0.6) +
#   scale_fill_manual(
#     values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
#     name = "Involvement"
#   ) +
#   scale_y_discrete(labels = y_labels) +
#   labs(
#     title = "Collecting and Discovery: Involvement by Person",
#     x = "Activity",
#     y = "Person"
#   ) +
#   theme_minimal(base_size = 12) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1),
#     axis.text.y = element_markdown(),   # renders the <span> highlight markup
#     panel.grid = element_blank(),
#     plot.title = element_text(face = "bold")
#   )
# 
# print(p_heatmap)
# ggsave("collecting_discovery_heatmap.png", plot = p_heatmap, width = 10, height = 6, dpi = 150)
```
```{r}
# library(readr)
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(stringr)
# 
# # --- Load data -----------------------------------------------------------
# df <- read_csv("capstone_data_correct_header.csv")
# 
# # --- Reshape: grab Person_title + all "Collecting and discovery_*" columns ---
# plot_df <- df %>%
#   select(Person_title, starts_with("Collecting and discovery_")) %>%
#   pivot_longer(
#     cols = -Person_title,
#     names_to = "Activity",
#     values_to = "Level"
#   ) %>%
#   mutate(
#     Activity = str_remove(Activity, "^Collecting and discovery_"),
#     Level = factor(Level, levels = c("RARE", "TOUCH", "DO"), ordered = TRUE)
#   )
# 
# # ============================================================================
# # HEATMAP  (Librarian_Me's label gets a yellow highlighter box -- plain
# # ggplot2 only, no ggtext. We hide the built-in axis labels and draw our
# # own text just left of the panel, with a colored rect behind the one we
# # want to highlight.)
# # ============================================================================
# highlight_person <- "Librarian_Me"
# 
# person_levels <- unique(plot_df$Person_title)
# plot_df <- plot_df %>%
#   mutate(Person_title = factor(Person_title, levels = person_levels))
# 
# n_people <- length(person_levels)
# highlight_y <- which(person_levels == highlight_person)
# 
# # Custom label positions (one per person), placed in the blank space we
# # create to the left of the panel via scale_x_discrete(expand = ...) below
# label_df <- data.frame(
#   Person_title = factor(person_levels, levels = person_levels),
#   x = -2.2
# )
# 
# # Adjust these two if the box doesn't fit your longest name / font size
# box_xmin <- -3.9
# box_xmax <- -0.6
# 
# p_heatmap <- ggplot(plot_df, aes(x = Activity, y = Person_title, fill = Level)) +
#   # Yellow highlighter box FIRST so it sits behind the text drawn later
#   annotate(
#     "rect",
#     xmin = box_xmin, xmax = box_xmax,
#     ymin = highlight_y - 0.4, ymax = highlight_y + 0.4,
#     fill = "#ffe600", color = NA
#   ) +
#   geom_tile(color = "white", linewidth = 0.6) +
#   geom_text(data = label_df, aes(x = x, y = Person_title, label = Person_title),
#             inherit.aes = FALSE, hjust = 1, size = 3.6) +
#   scale_fill_manual(
#     values = c("RARE" = "#fee5d9", "TOUCH" = "#fb6a4a", "DO" = "#a50f15"),
#     name = "Involvement"
#   ) +
#   # Reserve blank space on the left for our custom labels + highlighter box
#   scale_x_discrete(expand = expansion(add = c(4.3, 0.6))) +
#   labs(
#     title = "Collecting and Discovery: Involvement by Person",
#     x = "Activity",
#     y = NULL
#   ) +
#   theme_minimal(base_size = 12) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1),
#     axis.text.y = element_blank(),   # replaced by our own geom_text labels
#     axis.ticks.y = element_blank(),
#     panel.grid = element_blank(),
#     plot.title = element_text(face = "bold")
#   )
# 
# print(p_heatmap)
# ggsave("collecting_discovery_heatmap.png", plot = p_heatmap, width = 11.5, height = 6, dpi = 150)
```

